\subsubsection{AI}
\begin{center}

\setcounter{rc}{0}

  \begin{longtable}{| p{.5cm} | p{4.5cm} | p{4.5cm} | p{4.5cm} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Test Description}&
    \textbf{Expected Result}
    \\ \hline
    
    \rn &

    Imperial Units in the same environ as detected Rebel units may declare combat. &

    Test two things: 1) AI decides to attack the Rebel Units. 2) AI decides not to attack the Rebel Units &
    
    Both cases occur depending on game state.

    \\ \hline 

   \rn &

    If a character(s) engaged in combat wish to break off, they may attempt
    to do so. If successful, they are hidden and will take no further damage &

    Test two things: 1) AI attempts to break off from combat. 2) AI determines flight is futile and fights to the death. &

    Both cases occur depending on game state

    \\ \hline

    \rn & 

    A character engaged in a firefight may be captured or killed &

    Test two things: 1) AI attempts to capture an opponent. 2) AI attempts to kill the opponent. &

    Both cases occur depending on game state.

    \\ \hline

    \rn &

    AI can decide to search for a detected Rebel character or unit stack &

    Test two things: 1) AI searches for the Rebel unit(s) 2) AI doesn't search for the Rebel unit(s). &

    Both cases occur depending on game state.

    \\ \hline

    \rn &

    A unit can move between environs or planets. &

    AI moves a unit or character to a different environ/planet &

    The unit moves (and the outcome changes) based on game state.

    \\ \hline

    \rn &

    A player may assign a mission to a character &

    AI assigns a mission to a character. &

    The character is assigned the mission based on the game state and performs it best the character can.


    \\ \hline
  \end{longtable}
\end{center}
