\subsubsection{Combat}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{.5cm} | p{4.5cm} | p{4.5cm} | p{4.5cm} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Test Description}&
    \textbf{Expected Result}
    \\ \hline
    
    \rn &

    Rebel units spawned during rebellion immediately attack any
    imperial units they are able [10.7]. &

    Planet goes into state of rebellion and spawns rebel units in an
    environ where there are imperial forces. &
    
    Rebel units engage in combat with imperial forces. 

    \\ \hline 

    \rn &

    If a character stack in an environ is detecteda and there are no
    friendly military forces present, if they successfully break off
    from combat, they are no longer found and are no longer a part of
    combat [12.51]. &

    Break off from combat. &

    Character state is no longer found and combat is terminated.

    \\ \hline

    \rn & 

    If a character receives cumulative damage equal to their number of
    endurace points that character is dead and is removed from play
    [12.73]. &

    Engage in combat that results in enough wounds to match a
    character's endurance and assign those wounds to that character. &
    
    Character is removed from play.

    \\ \hline

    \rn &
    
    If attacking group is a squad, combat is firefight [12.31]. &

    Attack with squad and check combat type.&
    
    Combat type is firefight. 

    \\ \hline
    
    \rn & 
    
    Inactive characters do not contribute to combat rating or suffer
    damage [12.42]. &

    Engage in combat and set one character to inactive. &
    
    Character's stats do not contribute to combat rating and cannot
    have wounds assigned to them after battle.

    \\ \hline

    \rn & 
    
    Attacking character does not have inactive forces [12.44]. &

    Attack enemy forces. &

    No option to set inactive forces.

    \\ \hline

    \rn & 
    
    Leaders are not eliminated in military combat but if their forces
    are destroyed they are attacked by a squad [10.45]. &

    Engage in military combat with a leader where all forces are
    destoryd. &

    Leader is not destroyed but is attacked by a squad. 

    \\ \hline
    
    \rn &
    
    Characters stacked with military units are not effected by
    military combat and do not effect military combat but if their
    military units are eliminated, they are attacked by a squad
    [10.6]. &

    Engage in military combat with a stack containing characters where
    all military forces are eliminated. &

    Characters do not effect military combat and are not eliminated
    but are engaged in squad combat.

    \\ \hline

  \end{longtable}

\end{center}
