\subsubsection{Game Start}
\begin{center}

  \begin{longtable}{| p{.5cm} | p{4.5cm} | p{4.5cm} | p{4.5cm} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Test Description}&
    \textbf{Expected Result}
    \\ \hline
    
    1 &

    At game start, if player controls a planet, they may distribute
    characters and military forces on environs of those planest
    [16.12] &

    Player attempts to place a unit on the environ of a planet the
    player does not control &

    Unit does not occupy specified environ.  ??? Fail silently or
    notify player ???

    \\ \hline

    2 &

    At game start, if player does not control a planet, characters
    will "arrive from space" at the beginning of their operations
    phase. [16.12] &

    Player attempts to place units on environ of a planet they do not
    control &

    Unit does not occupy specified environ.  ??? Fail silently or
    notify player ???

    \\ \hline 

    3 &

    At game start, Imperial player places units first [16.14] &

    Rebel player attempts to place units \textit{before} Imperial
    player &

    Rebel player is unable to place forces.

    \\ \hline

    4 &

    At game start, Imperial player places units first [16.14] &

    Rebel player attempts to place units \textit{while} Imperial
    player \ is distributing their forces &

    Rebel player is unable to place forces.
    
    \\ \hline

    5 &
    Rebel game turn is first [16.14] &

    At start of game Imperial player attempts to begin turn
    \textit{before} Rebel player had begun turn &
    
    Imperial player is unable to begin turn.

    \\ \hline 

    6 &
    Rebel game turn is first [16.14] &

    At start of game Imperial player attempts to begin turn
    \textit{while} Rebel player is in thier turn &

    Imperial player is unable to begin turn.

    \\ \hline 

    7 &

    At start of game, all friendly units on the same environ are
    placed in the same stack [16.13]. &

    Try and create a second stack in an environ at the beginning of
    play &

    Second stack is not constructed.

    \\ \hline

    8 &

    At start of game, if rebel player has units to distribute, units
    placed must match environ type [16.13]. &

    Attempt to place rebel units in environ that does not match thier
    type. &

    User unable to place forces.

    \\ \hline 

  \end{longtable}

\end{center}
