\subsubsection{Missions}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{.5cm} | p{4.5cm} | p{4.5cm} | p{4.5cm} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Test Description}&
    \textbf{Expected Result}
    \\ \hline
    
    \rn &

    Diplomacy missions by a rebel player on a patriotic planet have 2
    bonus draws subtacted [13.2]. &

    Undergo diplomacy mission on a patriotic planet. &
    
    Total bouns draws are reduced by two. 

    \\ \hline 
    
    \rn &

    Diplomacy missions by a rebel player on a planet in descent have 1
    bonus draw added [13.2]. &

    Undergo diplomacy mission on a planet in descent. &
    
    Total bouns draws are increased by one. 

    \\ \hline

    \rn &

    Subvert troops, start rebel camp and scavenge missions can only be
    performed by the rebel player [13.2]. &

    During the missions phase as Imperial player, view available
    missions. &

    Scavenge, start rebel camp and subvert troops missions are not
    available options.

    \\ \hline 
    \rn &

    Diplomacy missions by a rebel player on a patriotic planet have 2
    bonus draws subtacted [13.2]. &

    Undergo diplomacy mission on a patriotic planet. &
    
    Total bouns draws are reduced by two. 

    \\ \hline 

    \rn &
    
    A rebel camp is equivalnet to a mission group for mission purposes
    [13.2]. &

    Assign rebel camp a mission in an environ during the mission
    phase. &

    Rebel is assigned mission. 

    \\ \hline

    \rn &
    
    Rebel camps cannot receive bonus draws [13.2]. &

    Draw action card resulting in a bonus draw with only a rebel camp
    doing missions in an environ. &

    No bonus draws are awarded. 

    \\ \hline 

    \rn &
    
    Rebel camps are never effected by the effects of an action card. &

    Perform mission with rebel camp and draw an action card resulting
    in combat. &

    Rebel camp does not engage in combat. 
 
    \\ \hline

    \rn &

    There can never be more than one rebel camp in an environ [13.2]. &

    Attempt start rebel camp mission in an environ with a rebel camp. &

    Mission is not available. 

    \\ \hline 

    \rn &
    
    Rebel camps cannot be moved [13.2]. &

    View movable units in an environ with a rebel camp during
    operations phase. &

    Rebel camp is not displayed. 

    \\ \hline 

    \rn &
    
    Characters cannot accompany rebel camps on a mission [13.2]. &

    Break mission stack into mission groups and attempt to add a
    character to a rebel camp mission group. &
    
    Character does not occupy rebel camp's mission group. 
    
    \\ \hline 

    \rn &

    Spaceship quest, summon soverign, question prisoner and steal
    resources missions are not available in the star system games
    [13.2]. &

    View available missions during missions phase of a star system
    game.&
    
    Spaceship quest, summon soverign, question prisoner and steal
    resources missions are not available.
    
    \\ \hline 

    \rn &

    Maximum number of action cards drawn for mission groups in an
    environ is equal to the environ size [13.3]. &

    Draw four action cards in an environ of size four. &

    Only bouns draws remain.

    \\ \hline  

    \rn &

    Bounus draws are only available is mission group has drawn maximum
    number of action cards for the environ size [13.3].&

    Quit missions in an environ of size 4 after drawing 1 action card
    when a character has bonus draws for the mission type. &

    No bouns draws available. 
    
    \\ \hline

    \rn &

    Action card must be resolved before mission letter can take effect
    [13.3]. &

    Die in combat with creatures resulting from an action card that
    would have otherwise resulted in mission success. &
    
    Mission does not succeed. 
    
    \\ \hline

    \rn &

    Except for the case of the NPP searching for characters on a mission, if
    an action drawn is the same as an action previously drawn in that
    environ, the action is ignored [13.42]. &

    Draw an action for creature combat after creature combat has
    already been resolved during that turn in that environ. &

    Mission group does not engage in creature combat. 

    \\ \hline

    \rn &

    In the case of an action card that allows the NPP to search for
    characters on a mission, this action may be repeated \textit{n}
    times where \textit{n} is the number of mission groups in that
    environ [13.48].  &

    Draw action card for two mission groups resulting in NPP search
    after NPP has already searched once in the environ.  &

    NPP performs search for mission groups in current mission environ.

    \\ \hline

    \rn &

    In the case of an action card that allows the NPP to search for
    characters on a mission, this action may be repeated \textit{n}
    times where \textit{n} is the number of mission groups in that
    environ [13.48].  &

    Draw action card for two mission groups resulting in NPP search
    after NPP has already searched twice in the environ. &

    NPP does not peform a search.    
    
    \\ \hline

    \rn &

    If an action card is drawn that contraticts an action drawn
    previously for a mission group in an environ in a turn, the
    contradtictory action is ignored [13.42]. &

    Draw an action card that prohibits bonus draws after drawing an
    action card that grants one extra bouns draw. &

    Extra bonus draw is kept, bonus draws are not prohibited. 

    \\ \hline
    
    \rn &

    If a single mission group is affected by an action card, that
    mission group is randomly chosen from all acvite mission groups in
    that environ [13.43]. &

    Draw action card resulting in creature combat in an environ
    containing two mission groups. &

    One of the two mission groups is chosen at random to engage in
    creature combat.
    
    \\ \hline

    \rn &

    If no creature is named by an environ the PP is attacked by sentry
    robots only if the NPP controls the planet [13.46]. &

    Draw creature attack in an environ where no creature is named and
    the NPP controls the planet. &

    Player engages in combat with sentry robots. 

    \\ \hline

    \rn &

    If no creature is named by an environ the PP is attacked by sentry
    robots only if the NPP controls the planet [13.46]. &

    Draw creature attack in an environ where no creature is named and
    the NPP does not control the planet. &

    Player does not engage in combat.
    
    \\ \hline
    
    \rn &

    If a planet is in a state of rebellion or in rebel control, the
    rebel player ignores irate locals attacks [13.47]. &

    As the rebel player performing a mission on a planet under rebel
    control, draw action card resulting in irate locals attack. &
    
    Player does not engage in combat. 
    
    \\ \hline

    \rn &

    If a planet is in a state of rebellion or in rebel control, the
    rebel player ignores irate locals attacks [13.47]. &

    As the rebel player performing a mission on a planet in rebellion,
    draw action card resulting in irate locals attack. &
    
    Player does not engage in combat. 
    
    \\ \hline
    
    \rn &

    If an action card is drawn that results in characters being found
    and there are NPP forces in that mission environ, the NPP's forces
    must attack one mission group. [12.15] &
    
    Draw an action card resulting in characters found in an environ
    where there are enemy fores. &

    Combat is intiated by either enemy characters or enemy squad at
    NPPs choice.

    \\ \hline
    
    \rn &

    If an action card is drawn that results in characters being found
    and there are no NPP forces in that mission environ, characters
    are not detected. [12.15] &
    
    Draw an action card resulting in characters found in an environ
    where there are no enemy fores. &

    Characters are not found. 

    \\ \hline

    \rn &

    Gather information mission cannot be performed on a planet under
    control of PP is there are NPP characters or military units in the
    mission environ [15.52]. &

    View available missions on a planet under PP control in an environ
    where NPP military or detected character forces are present &

    No gather information mission available. 

    \\ \hline

    \rn &

    Coup and diplomacy missions cannot be performed on a planet in a
    state of rebellion or under rebel control [15.57]. &

    View available missions on a planet in rebellion or under rebel
    control &

    No coup or diplomacy missions available. 

    \\ \hline

    \rn &

    If a planet's state is "rebellion stopped," the loyalty marker and
    the rebel-control marker are moved together [15.75]. &

    Complete mission that results in shifting loyalty marker. & 

    Rebel-control marker shifts with loyalty marker. 

    \\ \hline

    \rn &
    
    A coup mission requires a character with an intelligence rating of
    at least 1 [13.2]. &

    Attempt to assign a coup mission to a mission group without a
    character with an intelligence rating of at least 1. &

    Mission is not assigned to mission group. 

    \\ \hline

  \end{longtable}

\end{center}
