\subsubsection{Movement}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{.5cm} | p{4.5cm} | p{4.5cm} | p{4.5cm} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Test Description}&
    \textbf{Expected Result}
    \\ \hline
    
    \rn &

    Characters can only move from planet to planet using a spaceship
    [9.0]. &

    Attempt to move characters without a spaceship stacked with mobile
    military units. &

    Characters are left on the environ.

    \\ \hline 
    \rn &

    Every unit/character can be moved at most once during operations
    phase [9.0]. &

    Attempt to move a unit/character after moving it once. &

    Unit/character does not move.
    
    \\ \hline

    \rn &

    Non-phasing player may make a reaction move only once the phasing
    player is finished with their operations phase [9.0]. &

    Attempt to move NPP units before PP is done with operations
    phase. &

    NPP units do not move. 

    \\ \hline 

    \rn &

    Non-phasing player may make a reaction move only once the phasing
    player is finished with their operations phase [9.0]. &

    Attempt to move NPP units during PP's operations phase. &

    NPP units do not move.     
    
    \\ \hline

    \rn &
    
    Military units cannot move to an environ that is populated by a
    number of military units equal to it's size [9.5]. &

    Attempt to move a stack of one military unit to an environ
    populated by a max number of military units.&

    Military unit does not occupy environ.

    \\ \hline 

    \rn &
    
    A spaceship cannot carry more characters than it's capacity stat
    dictates [9.56]. &

    Construct a character stack with a spaceship that contains more
    characters than the capacity of the spaceship dictates. Attempt to
    move stack to another environ. &

    Only the number of characters equal to the capacity of the
    spaceship move.
    
    \\ \hline

    \rn &
    
    The non-phasing player may make a move for each environ containing
    PP military and detected forces [9.6]. &

    Enter reaction move phase when there are \textit{n} environs
    containing military units and detected forces. &

    Non-phasing player is allowed \textit{n} moves. 

    \\ \hline

    \rn &
    
    A reaction move cannot be made from one planet to another
    [9.61]. &

    Attempt to move a stack from planet to planet for a reaction
    move. &
    
    Stack does not occupy new environ.
    
    \\ \hline
    
    \rn &

    &

    &

    


    \\ \hline

  \end{longtable}

\end{center}
