\subsubsection{PDBs and Detection}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{.5cm} | p{4.5cm} | p{4.5cm} | p{4.5cm} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Test Description}&
    \textbf{Expected Result}
    \\ \hline
    
    \rn &

    Every planet has a PDB [8.0]. &

    Initialize galaxy. &
    
    Every planet has a PDB. 

    \\ \hline 
    \rn &

    The level of a PDB is  0, 1 or 2 [8.0]. &

    Initialize galaxy. &

    PDB levels conform to states 0, 1 or 2
    
    \\ \hline

    \rn &

    PDBs are either up or down [8.0]. &

    Initialize Galaxy. &

    PDBs conform to states up or down.

    \\ \hline 

    \rn &
    
    In Star System Games, the level of a PDB cannot be improved
    [8.13]. &

    ( ???? ) Succeed in a mission ( ???? ) that would improve PDB
    level. &
    
    PDB level does not improve.
    

    \\ \hline

    \rn &
    
    PDB can only be used if its status is "up" [8.2]. &

    Move characters from an environ on a planet where the PDB is down
    in a spaceship. &

    Characters do not undergo detection routine. 

    \\ \hline 

    \rn &
    
    If characters move across a planet without a spaceship they do not
    undergo the detection routine [9.0]. &

    Move character stack from one environ to another on the same
    planet. &
    
    Characters do not undergo detection routine. 
 
    \\ \hline

    \rn &

    If characters move across a planet with a spaceship may undergo a
    detection routine [9.0]. &

    Move character stack from one environ to another on a planet with
    a PDB up and at level 1 or higher .&

    Character stack undergoes detection routine. 

    \\ \hline 

    \rn &
    
    If a PDB incurs a loss of 2 when attacking it is placed in the
    "down" state [9.25]. &

    Incur a loss of 2 with an attacking PDB. &

    PDB state is "down."
 
    \\ \hline

    \rn &

    If a PDB incurs a loss of 3 when attacking it is placed in the
    "down" state \textit{and} it is reduced a level [9.25]. &

    Incur a loss of 3 with an attacking PDB. &

    PDB state is "down" \textit{and} level is decremented by 1.

    \\ \hline 

    \rn &
    
    A loss of 1 incurred by a PDB does nothing [9.25]. &

    Incur a loss of 1 with an attacking PDB. &
    
    PDB does not change state. 
 
    \\ \hline

    \rn &

    If a spaceship leaves a planet unable to conduct a detection
    routine, it and its characters are no longer detected [9.45]. &

    Move detected character stack in a spaceship from one environ to
    another on a planet unable to conduct a detection routine. &

    Characters are no longer detected. 

    \\ \hline 

    \rn &

    Stacks with military units are detected. &

    Move military units into a stack of undetected characters in an
    environ. &

    Characters are detected. 

    \\ \hline 

    \rn &

    If a detected character stack leaves an environ "undetected" by
    the enemy PDB they are no longer detected [9.31]. &
    
    Move detected character stack in a spaceship from an environ on a
    planet with an active PDB where the detection routine results in
    "undetected". &

    Characters are no longer detected. 
    Character stack is no longer detected. 

    \\ \hline 

    \rn &

    A PDB with a level 0 only detects regardless of the outcome of the
    detection routine [9.32]. &

    Undergo detection routine with a PDB at level 0 resulting in
    "eliminated." &

    Character stack is detected.

    \\ \hline 

    \rn & 

    Detected characters moving from one environ to another
    containing no detected characters or military units on the same
    planet without a spaceship are no longer detected [9.35]. & 

    Move detected characters to another environ on the same planet
    that contains no detected characters and no military units. &
    
    Characters are no longer detected. 

    \\ \hline 

    \rn &

    Military units are always detected but can be attacked by a PDB. &

    Move military units from space into a planet's environ. &

    Military units undergo detection routine and are subject to attack
    according to the military combat results table.
    
    \\ \hline 

    \rn &

    If a spaceship is "detected and damaged" twice in the same turn,
    the second "detected and damaged" outcome is equivalent to
    "eliminated" outcome [9.35]. &

    Move from one environ to another on a planet with an active PDB at
    level 1 or more and incur "detected and damaged" outcome twice. &

    Characters and spaceship are eliminated. 

    \\ \hline 

    \rn &

    In the star system games, if a detection routine results in
    "detected and damaged," the spaceship is eliminated when the
    destination is reached [9.31]. &

    Undergo detection routine that results in "detected and damaged" &
    
    Spaceship is eliminated on arrival. 

    \\ \hline 

    \rn &
    
    If a detection routine results in "eliminated," the spaceship and
    all characters on board are eliminated immediately [9.31]. &
    
    Undergo detection routine that results in "eliminated" &

    Spaceship and characters in it are eliminated. 
    
    \\ \hline 

  \end{longtable}

\end{center}
