\subsubsection{Planets and Control}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{.5cm} | p{4.5cm} | p{4.5cm} | p{4.5cm} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Test Description}&
    \textbf{Expected Result}
    \\ \hline
     
    \rn &

    At the beginning of play, every planet has a loyalty counter in 1
    of five states [15.1] &

    Check every planet's loyalty after game starts. &
    
    Loyalty counters are not null.  

    \\ \hline 
    \rn &

    A loyalty counter at patriotic cannot be increased further in the
    Imperial player's favor [15.13]. &
    
    Successful Imperial "Diplomacy" or "Political Tract" mission when
    loyalty counter is set to patriotic. &

    Loyalty counter does not change state. 
    
    \\ \hline

    \rn &

    A loyalty counter at unrest cannot be increased further in the
    Rebel player's favor [15.13]. &
    
    Successful Rebel "Diplomacy" or "Political Tract" mission when
    loyalty counter is set to patriotic. &

    Loyalty counter does not change state. 
   
    \\ \hline

    \rn &
    
    Loyalty counter on a planet in a state of rebellion or rebel
    control cannot be moved [15.14]. &

    Successful Rebel "Diplomacy" or "Political Tract" mission when
    planet is in a state of rebellion or rebel control. &

    Loyalty counter does not change state. 

    \\ \hline

    \rn &
    
    A planet in a state of rebellion is controlled by neither player
    [15.4]. &

    Put a planet in the state of rebellion. &

    "Control indicator" is in neither a rebel or imperial state.

    \\ \hline 

  \end{longtable}

\end{center}
