\subsubsection{Possessions}

\begin{center}

  \begin{longtable}{| p{.5cm} | p{4.5cm} | p{4.5cm} | p{4.5cm} |}
    \hline
    \textbf{\#} &
    \textbf{Rule Description} &
    \textbf{Test Description} &
    \textbf{Expected Result}
    \\ \hline
    
    1 &

    When rebel player receives a possession it must be immediately
    assigned to a character [14.11]. &

    Get possession as rebel character. &
    
    Prompt to assign possession to character. 

    \\ \hline 

    2 &

    When a rebel player receives a possession from a successful
    mission, the player must assign the possession to a character in
    that mission group [14.11]. &

    Get possession from mission and try to assign to character outside
    of mission group. &

    Character cannot receive possession.
    
    \\ \hline

    3 &

    Possessions are transferred between characters at the beginning of
    the missions phase [14.12]. &

    Attempt to transfer possession during operations phase. &

    Possession is not transferred. 

    \\ \hline 

    4 &
    
    Possessions may only be transferred between characters in the same
    environ [14.12]. &

    Attempt to transfer possession to character in another environ. &

    Possession is not transferred. 

    \\ \hline

    5 &
    
    A character may only have one companion possession at one time
    [14.13]. &

    Attempt to assign companion possession to character that already
    has a companion possession. &

    Character is not assigned companion possession. 

    \\ \hline 

    6 &
    
    A character may only have one spaceship possession at one time [14.13]. &

    Attempt to assign spaceship possession to character that already
    has a spaceship possession. &

    Character is not assigned spaceship possession. 
 
    \\ \hline

    7 &

    During star system game, if a possession becomes inoperative, it is
    lost [14.22]. &

    Set possession to inoperative. &

    Possession is removed from play. 

    \\ \hline 

    8 &

    If possession card states "lost after one use", it is returned to
    the possession card deck after use [14.23]. &

    Use possession that is lost after one use. &
    
    Possession is removed from character inventory and put back in
    possession deck.

    \\ \hline 

    9 &

    If a character is killed, any possessions besides spaceships are
    removed from play [14.25]. &

    Kill a character with possessions. Kill a character with a
    spaceship. &

    Possessions are lost and not returned to deck. Spaceship is not
    lost.
    
    \\ \hline

    10 &

    Destroyed possessions are not returned to the possession deck
    [14.26]. &

    Destroy a possession. &

    Possessions are lost and not returned to deck. 

    \\ \hline

    11 &

    If a rebel character is captured, their possessions, except for
    spaceships, are removed from play [14.26]. &

    Capture a rebel character. &

    Possessions are lost and not returned to deck. Spaceship is not
    lost.

    \\ \hline

    12 &

    A companion counts as a passenger on a spaceship [14.3]. &

    Attempt to add a character with a companion to a ship that has
    only one more spot available. &

    Character does not board ship.

    \\ \hline

  \end{longtable}

\end{center}
