\subsubsection{Searching}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{.5cm} | p{4.5cm} | p{4.5cm} | p{4.5cm} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Test Description}&
    \textbf{Expected Result}
    \\ \hline
    
    \newtc{Characters stacked with military units can be unstacked and then the characters can perform a search. [11.21]}
    {Attempt to perform character search with a character stacked with
    military.}
    {Search is not conducted}
    
    \newtc{-}
    {Attempt to perform character search with no character stacked with military.}
    {Search allowed.}
    
    \newtc{Characters stacked with military units cannot be searched. [11.1]}
    {Attempt to search for characters stacked with military units.}
    {Search fails}
    
    \rn &
    
    Search is conducted with either military units or
    characters. Characters stacked with military units cannot be used
    to conduct character search unless they are moved from the
    military stack [11.21]. &

    Attempt to perform character search with a character stacked with
    military. &

    ??? Either search is not conducted or a military search is
    conducted instead. ???

    \\ \hline 

    \rn &

    Only the units in a successful search group may attack [11.23].&

    Successfully search with characters and choose combat. & 

    Character combat is initiated.
    
    \\ \hline
    
    \newtc{Using characters to search results in their detection [11.31].}
    {Search with undetected characters.}
    {Characters become detected.}
    
    \newtc{Searching may only be done in environs where a player has units
    and there are \textit{detected} enemy forces [11.1].}
    {Attempt to search an environ where there are no detected forces.}
    {No search is conducted.}

  \end{longtable}
\end{center}
