\subsubsection{Stacking}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{.5cm} | p{4.5cm} | p{4.5cm} | p{4.5cm} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Test Description}&
    \textbf{Expected Result}
    \\ \hline
    
    \rn &

    Number of military units in a stack, in an environ can never
    exceed the environ size [9.5] &

    Try and place a military unit in an environ that is at capacity &
    
    Military unit is not added to the stack.

    \\ \hline 
    \rn &

    There is no limit to the number of units in a stack [9.5]. &
    
    Construct an artificial stack out of all military units + all
    characters + all ships&
    
    All units, characters, ships occupy the same stack.
    
    \\ \hline

    \rn &

    At the end of the operations phase, an environ may have at most
    two stacks, one with characters eligible for missions and their
    spaceships and another for the rest of the player's forces
    [9.5]. &

    Attempt to end operations phase with three stacks in an environ &

    ??? Combine forces automatically or prompt user to refactor
    forces??? [16.14]

    \\ \hline 

    \rn &

    Character's stacked with military units must have leadership
    rating of at least 1 to be named leader [9.52]. &

    Attempt to name leader with less than 1 leadership rating. &
    
    Character does not assume leadership of stack.

    \\ \hline

    \rn &

    If a stack has no military units and multiple spaceships, the each
    spaceship must move as a separate stack and undergo any detection
    routines accordingly [9.54]. &

    Attempt to move a stack with two spaceships and no military
    units. &
    
    Movement is not allowed until a spaceship is specified. 

    \\ \hline 

    \rn &
    
    A spaceship may not be moved unless it is stacked with military
    units or a character with navigation rating of 1 or higher
    [9.55]. &

    Attempt to move a spaceship stacked with only a character with
    navigation rating less than 1 &

    Spaceship does not move.

 
    \\ \hline

    \rn &

    If at the end of the operations phase, a character is not stacked
    in the mission stack, character cannot perform missions during the
    missions phase [9.57]. &

    During missions phase, attempt to add character not stacked in the
    mission stack to a mission group. &
    
    Character is not added to mission group.

    \\ \hline 

  \end{longtable}

\end{center}
