\section{Control}

% status : completed, except for determining who controls the planet

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{.5cm} | p{10.0cm} | p{2.0cm} | p{2.5cm} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric Value}
    \\ \hline
    
    \rn &
    
    Attack by Sentry robots only occurs if the non-phasing player controls the planet. &
    
    13.46, 15.51 &
    
    - 
    
    \\ \hline
    
    \rn &
    
    Gather information mission cannot be performed on a planet under control of the phasing player if there are enemy character or military units present. &
    
    15.52 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If the Imperial player has less spaceships in play than at the beginning of the game and has any Imperial Knight on an Imperial?controlled planet, that Imperial player can received a spaceship, which is stacked with the Imperial Knight up to the beginning of the play limit. &
    
    14.61 &
    
    - 
    
    \\ \hline
    
    \rn &
    
    The number of spaceships received from rule 14.61 is limited by the number of starships obtained at the beginning of the play limit. &
    
    15.73 &
    
    -
    
    \\ \hline
    
    \rn &
    
    Characters do not have any effect and are ignored in determining who controls the planet. &
    
    15.74 &
    
    - 
    
    \\ \hline
    
    \rn &
    
    Neither player may perform “Coup” or “Diplomacy” missions if the planet is in a state of Rebel controlled. &
    
    15.75 &
    
    - 
    
    \\ \hline
    
    \rn &
    
    If a planet’s loyalty is shifted when a planet is in a state of Rebellion Stopped, the Loyalty marker and Rebel?control marker are moved together.  & 
    
    15.75 &
    
    - 
    
    \\ \hline
    
    \rn &
    
    A planet must be in one of four states: "Imperial Control", "Rebellion", "Rebel Control", "Rebellion Stopped". &
    
    15.5 &
    
    -
    
    \\ \hline
    
    \rn &
    
    Actual control of a planet is determined by military units and status of PDB. &
    
    15.5 &
    
    -
    
    \\ \hline
    
    \rn &
    
    Control of a planet may change at any time. &
    
    15.5 &
    
    -
    
        
    \\ \hline
  \end{longtable}
\end{center}