\section{Creature and Irate Locals}

% status : in progress

\subsection{General}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{\first} | p{\second} | p{\third} | p{\fourth} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric}
    \\ \hline
    
    \newrule{The description of any creature overrides any general rule of the game.}{13.45}{-}
    
    \newrule{Creature stats and descriptions are found in the Galactic Guide.}{13.45}{-}
    
    \newrule{Creatures are used during an action card that states a creature attacks (See Galactic Guide)}{5.3K}{-}
    
    \newrule{Creatures are only spawned on environs in which they are listed.}{5.3K}{-}

    \newrule{If no creature is named on the environ during a “Creature Attacks” event, the card may state that the mission group is attacked by one or sentry robots.}{13.46}{-}
    
  \end{longtable}
\end{center}

\subsection{Character Combat and Creatures/Irate Locals}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{\first} | p{\second} | p{\third} | p{\fourth} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric}
    \\ \hline
    
    \newrule{Character combat involving creatures only occurs when the “Creature attacks one Mission Group” event card is drawn.}{12.12}{-}
    
    \newrule{Character combat involving irate locals only occurs when the “Irate Locals attack one Mission Group” event card is drawn.}{12.13}{-}
    
    \newrule{The creature is considered the attacking force in creature combat.}{12.10}{-}
    
    \newrule{Irate locals are considered the attacking force in irate locals combat.}{12.10}{-}
    
    \newrule{Character combat involving creatures is resolved immediately.}{12.12}{-}
    
    \newrule{Character combat involving irate locals is resolved immediately.}{12.13}{-}
    
    \newrule{Only one character mission group is attacked.}{12.2}{-}
    
    \newrule{If more than one character mission groups are present in the environ, the mission group attacked is chosen at random.}{12.2}{-}
    
    \newrule{Combat involving irate locals may be “firefight” or “hand?to?hand” as determined by the Irate Locals chart.}{12.31}{-}
    
    \newrule{The intention of combat involving creatures is always “kill”.}{12.32}{-}
    
    \newrule{The intention of combat involving irate locals is always “kill”.}{12.32}{-}
    
  \end{longtable}
\end{center}