\section{Detection}

% status : in progress

\subsection{Detection using a PDB}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{\first} | p{\second} | p{\third} | p{\fourth} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric}
    \\ \hline
    
    \rn &
    
    The PDB can be used to attempt detection of Enemy characters entering, leaving, or traveling on the planet in a spaceship &
    
    8.2 &
    
    - 
    
    \\ \hline
    
    \rn &
    
    PDB can attempt to detect enemy spaceships when an enemy spaceship leaves or arrives on a planet with a PDB with an “up” status and under control of the non?phasing player &
    
    9.3 &
    
    -
    
    \\ \hline
    
    \rn & 
    
    The outcome of the detection is one of the following four results: “Undetected”, “Detected”, and “Detected and Damaged”, and “Eliminated”. & 
    
    9.31 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If the outcome of the detection is “Undetected”, undetected units can continue movement and detected units become undetected and can continue movement. &
    
    9.31 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If the outcome of the detection is “Detected” all characters in the spaceship have a status now of “detected” and movement continues &
    
    9.31 &
    
    -
        
    \\ \hline
    
    \rn &
    
    If the outcome of the detection is “Detected and Damaged”, all the characters in the spaceship have a status of “detected”. &
    
    9.31 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If the outcome of the detection is “Detected and Damaged”, the spaceship is eliminated when the destination is reached (No effect on the passengers). &
    
    9.31 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If the outcome of the detection is “Eliminated”, the spaceship and all characters on board are eliminated. &
    
    9.31 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If the PDB has a level of 0 (and status of “up”), the PDB may still detect an enemy spaceship, however, the outcomes of “Detected and Damaged” and “Eliminated” are treated as an outcome of “Detected” &
    
    9.31 &
    
    -
    
    \\ \hline
    
    \rn &
    
    A “down” PDB cannot be used for detection. &
    
    9.32 &
    
    -
    
    \\ \hline
    
    \rn &
    
    Detection against the same spaceship may be done twice (i.e. move from and to a planet controlled by an enemy PDB) & 
    
    9.33 &
    
    -
    
    \\ \hline
    
    \rn &
    
    Movement from one environ to another on the same planet can be detected just once. &
    
    9.33 &
    
    -
    
    \\ \hline
    
    \rn &
    
    Military units or characters specifically never undergo detection. &
    
    9.34 &
    
    -
    
    \\ \hline
    
    \rn &
   
   A stack with military units are considered detected with regards to enemy PDBs. &
   
   9.52 &
   
   -
   
   \\ \hline
   
   \rn &
   
   Each spaceship much be detected separately. & 
   
   9.54 &
   
   -
   
   \\ \hline

    
  \end{longtable}
\end{center}

\subsection{Movement and Detection}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{\first} | p{\second} | p{\third} | p{\fourth} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric}
    \\ \hline
    
    \rn &
    
    Detected players moving from one environ to another on the same planet without a spaceship change status from “detected” to “undetected” if no detected characters are in the destination environ &
    
    9.35 &
    
    - 
    
    \\ \hline
    
    \rn &
    
    If a spaceship receives two outcomes of “Detected and Damaged” in one turn, upon the second “Detected and Damaged” result, the outcome is considered to be “Eliminated”. &
    
    9.35 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If “undetected” characters move to an environ with “detected” characters, those “undetected” characters become “detected”. &
    
    9.4 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If “detected” characters move to an environ with “undetected” characters, the “undetected” characters become “detected”. &
    
    9.4 &
    
    -
    
    \\ \hline
    
    \rn &
    
    Enemy can make a reaction move due to “detected” characters and may conduct a search for those characters during the Search Phase & 
    
    9.41 &
    
    -
    
    \\ \hline
    
    \rn &
    
    Characters may be detected due to events on an action card when resolving mission or due to a search. & 
    
    9.42 &
    
    -
    
   \\ \hline
   
   \rn &
   
   Assassination mission can only be performed against a detected enemy character. &
   
   9.44 &
   
   -
   
   \\ \hline
   
   \rn &
   
   If a spaceship leaves a planet and is ineligible to conduct the Detection Routine, the spaceship and all characters are no longer detected. & 
   
   9.45 &
   
   -
   
   \\ \hline


  \end{longtable}
\end{center}

\subsection{Detection and Searching}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{\first} | p{\second} | p{\third} | p{\fourth} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric}
    \\ \hline
    
    \rn &
    
    When a player uses characters to search, those characters are automatically detected. &
    
    11.31 &
    
    - 
    
    \\ \hline

  \end{longtable}
\end{center}    
