\section{Healing}

% status : in progress

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{.5cm} | p{10.0cm} | p{2.0cm} | p{2.5cm} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric Value}
    \\ \hline
    
    \rn &
    
    Characters who are stacked with military units, characters who are guarding prisoners, or healing cannot go on missions. &
    
    13.7 &
    
    - 
    
    \\ \hline
        
    \rn &
    
    Healing occurs if the character with wounds does nothing for the player’s entire turn.
    
    13.71 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If a character leads military units, pilots a character spaceship, moving from one environ to another without a spaceship, the character is not healed (not a complete list?) &
    
    13.71 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If a characters is a passenger in a character spaceship or moved with military units, this does not prohibit healing. & 
    
    13.71 &
    
    \\ \hline
    
    \rn &
    
    All wounds of a character are automatically healed if the character meets the requirements for healing. &
    
    13.71 &
    
    \\ \hline
    
    \rn &
    
    Doctor Sontag and the “Medi-Kit of Ptolus” can heal characters of wounds only during the Rebel player’s turn. & 
    
    13.72 &
    
    \\ \hline
    
    \rn &
    
    Any wounded Rebel characters stacked with Doctor Sontag at the beginning of the player turn are immediately healed at the beginning of the Rebel player’s turn. & 
    
    13.72 &
    
    -
    
    \\ \hline
    
    \rn &
    
    Any character in possession of the “Medi-kit of Ptolus” will be healed at the beginning of that player’s turn. &
    
    13.72 &
    
    -
    
    \\ \hline
    
    \rn &
    
    Doctor Sontag or the Medi-kit can only be used at the beginning of the Rebel player’s turn (before any other action).  &
    
    13.72 &
    
    -
    
    \\ \hline
    
    \rn &
    
    Doctor Sontag can perform mission in the turn in which he heals. & 
    
    13.72 &
    
    -
    
    \\ \hline
    
    \rn &
    
    Doctor Sontag can heal himself.  &
    
    13.72 &
    
    -
    
    \\ \hline
    
  \end{longtable}
\end{center}