\section{Military Units}

% status : finished?

\subsection{Rebel}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{\first} | p{\second} | p{\third} | p{\fourth} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric}
    \\ \hline
    
    \rn &
    
    Rebel military units only have values of ‘1-0’ and ‘2-1’. &
    
    7.3 & 
    
    1
    
    \\ \hline
    
    \rn &
    
    Units with stats of ‘2-1’ are considered mobile. &
    
    7.3 &
    
    1
    
    \\ \hline
    
    \rn &
    
    Units with stats of ‘1-0’ are not mobile so cannot leave the planet by themselves. &
    
    7.3 &
    
    3
    
    \\ \hline
    
    \rn &
    
    Rebel military units are never hidden. &
    
    7.3 &
    
    3
    
    \\ \hline
    
    \rn &
    
    For each value, Rebel units come in each type of environ. &
    
    7.31 &
    
    2
    
    \\ \hline
    
    \rn &
    
    Rebel military units have the type of the environ in which they are created. &
    
    7.32 &
    
    2
    
    
    \\ \hline
    
    \rn &
    
    Rebel military units are not confined to the type of environ in which they were created. &
    
    7.32 &
    
    1
    
    \\ \hline
    
    \newrule{Rebel military units with stats of '2-1' may move from any environ to any other in the Star System}{7.3}{10}
    
  \end{longtable}
\end{center}

\subsection{Imperial}

% status : started

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{\first} | p{\second} | p{\third} | p{\fourth} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric}
    \\ \hline
    
    \newrule{Imperial player has only military types of Militia, Patrol, and Line.}{7.2}{1}
    
    \newrule{The Militia has a strength of 1-0.}{7.2}{1}
    
    \newrule{Patrol has a strength of 1-2.}{7.2}{1}
    
    \newrule{Line has a strength of 3-2.}{7.2}{1}
    
    \newrule{Militia units are always shown, never hidden.}{7.21}{3}
    
    \newrule{Militia cannot leave a planet.}{7.21}{3}
    
    \newrule{Patrol and Line are deployed in “mobile” status.}{7.22}{1}
    
    \newrule{Patrol and Line strength is revealed when used and then rehidden.}{7.22}{2}
    
    \newrule{Patrol and Line strength only hidden from Rebel player.}{7.22}{1}
    
    \newrule{Patrol and Line may move from any environ to any other in the Star System}{7.23}{10}
    
        
  \end{longtable}
\end{center}