\section{Mission}

All missions in an environ are independent of all other missions in other environs. Each environ is resolved before going to the next environ.
The maximum number of action cards in TOTAL for all missions in the environ is equal to the environ size, i.e. the environ size does not apply just to individual groups. Also, if ANY resolved action card contains the mission letter of ANY active mission group in that environ, that mission is then considered completed (except for 13.51 missions, see below). Also, the effect of the action card is on a RANDOM active mission group (See [13.5]).

\subsection{General}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{\first} | p{\second} | p{\third} | p{\fourth} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric}
    \\ \hline
    
    \newrule{Missions are performed during the Mission phase.}{13.0}{-}
    
    \newrule{Missions are selected from available mission cards.}{13.0}{-}
    
    \newrule{Missions are only performed by characters.}{13.0}{-}
    
    \newrule{Mission are performed only in the environ in which a phasing player’s character(s) are located.}{13.0}{-}
    
    \newrule{Missions are resolved by Action cards.}{13.0}{-}
    
    \newrule{Each mission is completely resolved one environ at a time before preceding to the next environ.}{13.0}{-}
    
    \newrule{The Order of the environs is up to the phasing player.}{13.0}{-}
    
    \newrule{Characters cannot be moved from a non?mission stack during the mission phase, i.e. a mission stack is required at the end of the previous phase}{ }{-}
  
  \newrule{All eligible characters might be assign to one mission, each character to separate missions, or any combination in between.}{13.1}{-}
  
  \newrule{Each character can only be assigned to one mission during each mission phase.}{13.1}{-}
  
  \newrule{Some missions are only available one player.}{13.1}{-}
  
  \newrule{Some missions require certain environ conditions.}{13.1}{-}
  
   \newrule{Environ type determines which section of the Action card to use.}{5.3J}{-}
   
   \newrule{The following are not available during the Star System game: “Spaceship Quest”, “Summon Sovereign”, “Question Prisoner”, and “Steal Resources”.}{13.2}{-}
   
    \newrule{The maximum number of cards a mission group may draw is the environ size.}{13.3}{-}
    
    \newrule{The mission groups may stop drawing action cards at any time.}{13.3}{-}
    
    \newrule{Each card is resolved immediately, before the next one can be drawn.}{13.3}{-}
    
    \newrule{Bonus draws are only available if the mission group has drawn the maximum number of action cards available limited by the environ size.}{13.3}{-}
    
    \newrule{The action card must be resolved before the mission letters on the card take effect.}{13.3}{-}
    
    \newrule{If the mission group is eliminated during an action card effect, the mission letter does not take effect.}{13.3}{-}
    
    \newrule{Each action card has three sections: “urban”, “special”, and “wild”.}{13.32}{-}
    
    \newrule{For missions occurring in an environ of type “urban”, use the “urban” section of the action card only.}{13.32}{-}
    
    \newrule{For missions occurring in an environ of type “wild”, use the “wild” section of the action card only.}{13.32}{-}
    
    \newrule{For missions occurring in an environ of type “subterranean”, “liquid”, “air”, or “fire”, use the “special” section of the action card only.}{13.32}{-}
    
    \newrule{An action card is only considered if any mission type mentioned is being performed on that environ.}{13.41}{-}
    
    \newrule{If the action drawn is the same as a previously drawn action, the action drawn is ignored (except [13.48]).}{13.42}{-}
    
    \newrule{If the action drawn contradicts a previously drawn action, the action drawn is ignored. [13.42] Action draws ignored do not count towards any limit, etc.}{ }{-}
    
    \newrule{If a single mission group is affected by an action card, that mission group is randomly chosen from all active mission groups in that environ.}{13.43}{-}
    
    \newrule{If an event aborts a mission, that mission group is no longer effected by an action card effects.}{13.44}{-}
    
    \newrule{If an event aborts a mission, that mission group is no longer effected by bonus draws.}{13.44}{-}
    
    \newrule{The description of any monster overrides any general rule.}{13.45}{-}
    
    \newrule{The characters of a group that have successfully completed a mission are no longer take part in action draws.}{13.5}{-}
    
    \newrule{If there are other mission groups still attempting to complete their missions, they continue drawing cards up to the limit of the environ size.}{13.5}{-}
    
    \newrule{Bonus draws only occur after the maximum number of actions cards have been resolved due to the environ size.}{13.6}{-}
    
    \newrule{Bonus draws only apply to the mission group performing the mission.}{13.6}{-}
    
    \newrule{Bonus draws are all drawn at once.}{13.6}{-}
    
    \newrule{The effects of bonus draws are ignored.}{13.6}{-}
    
    \newrule{Each active mission group can take bonus draws equal to the amount specified by the mission card plus bonus.}{13.6}{-}
    
    \newrule{Even if a mission card does not specify a bonus number, if a bonus applies, bonus draw(s) are still available.}{13.6}{-}
    
   \newrule{Bonus draws bonuses can come from a character’s special characteristic or an event that allows an extra bonus draw.}{13.6}{-}
   
   \newrule{Characters who are stacked with military units, characters who are guarding prisoners, or healing cannot go on missions.}{13.7}{-}
   
    \newrule{The following missions allow different degrees of success (depending on how many of the appropriate Mission Letters the Player draws): Coup (C), Diplomacy (D), Free Prisoners (F), Gather Information (I), Stop Rebellion (R), Sabotage (S), Subvert Troops (T).}{13.5}{-}
    
    \newrule{The missions above (those listed in [13.5]), is not required to consider the mission completed when drawing the appropriate mission letter (in contradiction to [13.5]).}{13.51}{-}
    
    \newrule{By continue performing the missions (of those listed in [13.5]), the player hopes to get a second or third, etc. mission letter in gaining the effects as listed on the missions cards.}{13.51}{-}  
    
    \newrule{If the player chooses to continue the missions listed in [13.51], the mission is not considered complete and the effects are NOT implemented.}{13.51}{-}
    
    \newrule{If a continuing mission (of [13.51]), is aborted, the mission is not considered completed and the effects of the mission are not implemented.}{13.51}{-}
    
    \newrule{If all the characters in the mission group at killed or captured, the mission is not considered completed and the effects of the mission are not implemented.}{13.52}{-}
    
    \newrule{The decision to stop a continuing mission occurs after an action card has been resolved and before the next one is drawn.}{13.52}{-}
    
    \newrule{If a continuing mission is stopped, the mission is considered complete and all accumulated results happen.}{13.52}{-}
    
    \newrule{If no more action cards can be drawn (due to the environ size), a continuing mission is considered complete and all accumulated results happen.}{13.52}{-}
    
    \newrule{Bonus draws can be used for continuing missions.}{13.52}{-}

  
  \end{longtable}
\end{center}


\subsection{Specific}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{\first} | p{\second} | p{\third} | p{\fourth} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric}
    \\ \hline
    
    \newrule{Coup mission requires at least one character with an intelligence rating greater than one.}{13.2}{-}
    
    \newrule{If the coup mission is successful, the coup mission cannot be attempted again on the same environ.}{13.2}{-}
    
    \newrule{Coup mission cannot be performed on an environ that has already been in coup or does not have a coup rating.}{13.2}
    
    \newrule{The coup rating of the environ is used when performing the coup mission.}{5.3I}{-}
    
    \newrule{Only the Gather Information mission directly affects victory points.}{13.2}{-}
    
    \newrule{A diplomacy mission is effected by the planets loyalty status.}{13.2}{-}
    
    \newrule{If the diplomacy mission is being attempted by a Rebel player with on a patriotic planet, 2 bonus draws are subtracted. For a planet in decent, one bonus draw is added.}{13.2}{-}
    
    \newrule{Since there are no sovereigns in the star system game, there are no bonuses to the diplomacy mission from their presence.}{13.2}{-}
    
    \newrule{The subvert troops and scavenge mission can only be performed by the rebel player.}{13.2}{-}
    
    \newrule{“Start Rebel Camp” (B) can only be performed by the rebel player.}{13.2}{-}
    
    \newrule{An established rebel camp can performed missions: C, D, F, I, S, and T.}{13.2}{-}
    
    \newrule{A rebel camp is equivalent to a character for mission purposes.}{13.2}{-}
    
    \newrule{Rebel camp never receives bonus draws.}{13.2}{-}
    
    \newrule{Rebel camp is never effected by the effects of action cards no matter what the contents.}{13.2}{-}
    
    \newrule{Only at most one rebel camp can occupy an environ.}{13.2}{-}
    
    \newrule{A rebel camp cannot be moved.}{13.2}{-}
    
    \newrule{Characters cannot accompany the rebel camp on any mission.}{13.2}{-}
    
    \newrule{When aborted by an action card during the “Assassination” (A) mission, the mission group does not roll to see how the group is affected.}{13.2}{-}
    
    \newrule{If no creature is named on the environ during a “Creature Attacks” event, the card may state that the mission group is attacked by one or more sentry robots.}{13.46}{-}
    
    \newrule{During an “Irate locals attacks” event, the race is determined by the environ and the stats by the “Irate Locals Chart”.}{13.47}{-}
    
    \newrule{If more than one race is named, use the first on listed on the “Irate Locals Chart.”}{13.47}{-}
    
    \newrule{If the planet is currently in rebellion or rebel?controlled, ignore the event if the Rebel player is conducting the mission.}{13.47}{-}
    
    \newrule{After the action has been performed (assuming the mission group is still alive?), if any mission letters corresponding to the mission the group is performing is found, the mission is completed effective immediately (Except those missions listed in 13.51).}{13.5}{-}
       
   \newrule{Player may obtain possessions from a “Scavenge for Possessions” mission.}{14.1}{-}
   
   \newrule{Gather information mission cannot be performed on a planet under control of the phasing player if there are enemy character or military units present.}{15.52}{-}
   
   \newrule{If during the action event, “Coup Mission aborted”, or the failure to complete an “Assassination” mission, there are no enemy units in the same environ, the characters are not captured.}{12.87}{-}
     
  \end{longtable}
\end{center}