\section{PDB}
\label{sub:pdb}

% status : started

\subsection{General PDB}
For rules regarding detection, see section \ref{sub:detection}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{\first} | p{\second} | p{\third} | p{\fourth} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric}
    \\ \hline
    
    \newrule{The PDB is controlled by the player who controls the planet.}{8.0}{-}
    
    \newrule{Every planet has a PDB.}{8.0}{-}
    
    \newrule{The level of the PDB is one of the following values: 0,1,2.}{8.0}{-}
    
    \newrule{The PDB can have status of “up” or “down”.}{8.0}{-}
    
    \newrule{A status of “up” means functional and a status of “down” means not functioning.}{8.0}{-}
    
    \newrule{If the planet is not in control of either player, the PDB cannot be used by any player.}{8.33}{-}
    
    \newrule{The level of a PDB cannot be improved.}{8.13}{-}
    
    \newrule{A PDB can be used to attempt detection of Enemy characters entering, leaving, or traveling on the planet in a spaceship.}{8.2}{-}
    
    \newrule{The PDB can only be used if the status is “up”.}{8.2}{-}
    
    \newrule{A PDB with a status of “down” cannot be used for any purpose.}{8.2}{-}
    
    \newrule{The PDB can change to “down” status due to “Sabotage Mission” (n53), Action Event “Locals Raid” (n70).}{8.31}{-}
    
    \newrule{If units move from environ to another environ on the same planet, the PDB cannot be used for detection.}{9.0}{-}
    
    \newrule{If characters move across the planet without a spaceship, the PDB cannot be used for detection.}{9.0}{-}
    
    \newrule{If the characters move across the planet with a spaceship, the characters are considered to be in the spaceship and can be detected.}{9.0}
    
  \end{longtable}
\end{center}
    
\subsection{PDB Combat}
\label{sub:pdbcombat}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{\first} | p{\second} | p{\third} | p{\fourth} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric}
    \\ \hline
    
    \newrule{Military combat does not occur against spaceships.}{9.21}{-}
    
    \newrule{An attack by a Level 2 PDB is resolved using 3?1 column of the table.}{9.22}{-}
    
    \newrule{An attack by a Level 1 PDB is resolved using the ‘1?1’ column of the table.}{9.22}{-}
    
    \newrule{A level 0 PDB cannot be used to attack.}{9.22}{-}
    
    \newrule{Surviving moving units can continue movement.}{9.24}{-}
    
    \newrule{If PDB incurs a loss of 2 when attacking, it is placed in “down” status.}{9.25}{-}
    
    \newrule{If PDB incurs a loss of 2 when attacking, it is placed in “down” status.}{9.25}{-}
    
    \newrule{If PDB incurs a loss of 3 when attacking, it is placed in “down” status and reduced a level.}{9.25}{-}
    
    \newrule{A loss of 1 has no effect on a PDB.}{9.25}{-}
    
    \newrule{A unit cannot attack an enemy PDB.}{9.26}{-}
    
    \newrule{Due to movement restrictions, a unit can be attacked/detected at most twice during the movement turn (when leaving and then entering an environ on another planet).}{9.27}{-}
    
    \newrule{If a spaceship leaves a planet and is ineligible to conduct the Detection Routine, the spaceship is no longer detected.}{9.45}
    
    \newrule{A stack with military units are considered detected with regards to enemy PDBs.}{9.52}{-}
    
  \end{longtable}
\end{center}
