\section{Possessions}

% status : finished?

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{\first} | p{\second} | p{\third} | p{\fourth} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric}
    \\ \hline
    
    \rn &
    
    There are 20 possessions in the game. &
    14.0 &
    
    3
    
    \\ \hline
    
    \rn &
    
    There are 4 types of possessions: character spaceships, weapons, objects, and companions. &
    
    14.0 &
    
    2
    
    \\ \hline
    
    \rn &
    
    Possessions are only used by the rebel player. &
    
    14.0 &
    
    3
    
    \\ \hline
    
    \rn &
    
    Possessions are obtained during the course of the game, or the beginning of the game. &
    
    14.0 &
    
    2
    
    \\ \hline
    
    \rn &
    
    The imperial spaceship is not a possession. & 
    
    14.0 &
    
    3
    
    \\ \hline
    
    \rn &
    
    The imperial spaceship can only be used by the imperial player. & 
    
    14.0 &
    
    2
    
    \\ \hline
    
    \rn &
    
    Player may obtain possessions from a “Scavenge for Possessions” mission. &
    
    14.1 &
    
    6
    
    \\ \hline
    
    \rn &
    
    When the rebel player receives a possession, it must be immediately assigned to a character. &
    
    14.11 &
    
    4
    
    \\ \hline
    
    \rn &
    
    If a possession is obtained at the beginning of the game, that possession may be assigned to any Rebel character. &
    
    14.11 &
    
    3
    
    \\ \hline
    
    \rn &
    
    If a possession is obtained during the game due to a mission, it must be assigned to a character in that mission group. &
    
    14.11 &
    
    4
    
    \\ \hline
    
    \rn &
    
    Possessions may be transferred at the beginning of the rebel mission phase, never during. & 
    
    14.12 &
    
    3
    
    \\ \hline
    
    \rn &
    
    A character may possess any number of weapons and object possessions. &
    
    14.13 &
    
    2
    
    \\ \hline
    
    \rn &
    
    A character may only have one companion possession (regardless of other possessions).  &
    
    14.13 &
    
    2
    
    \\ \hline
    
    \rn &
    
    A character may only have one spaceship (regardless of other possessions). &
    
    14.13 &
    
    2
    
    \\ \hline
    
    \rn &
    
    Until the possession is used, the possession may be kept secret. & 
    
    14.2 &
    
    2
    
    \\ \hline
    
    \rn &
    
    If the possession card states, “Never needs repair”, the possession maybe used as many times as the rebel player wishes. &
    
    14.1 &
    
    4
    
    \\ \hline
    
    \rn &
    
    If the possession card states, “May become inoperative after use”, every time the possession is used, a random number 1-6 is generated. Based on the card, the possession either becomes inoperative, or it is able to be used again. & 
    
    14.22 &
    
    3
    
    \\ \hline
    
    \rn &
    
    During the star system game, if the possession is inoperative, it is lost. &
    
    14.22 &
    
    2
    
    \\ \hline
    
    \rn &
    
    If the possession card states, “Lost after one use”, it is returned to the possession deck after use. &
    
    14.23 &
    
    2
    
    \\ \hline
    
    \rn &
    
    Lost possession are returned to the possession deck. & 
    
    14.24 &
    
    2
    
    \\ \hline
    
    \rn &
    
    Drawing a possession is random. &
    
    14.24 &
    
    1
    
    \\ \hline
    
    \rn &
    
    Possessions of a killed character are destroyed (except spaceships). &
    
    14.25 &
    
    2
    
    \\ \hline
    
    \rn &
    
    Destroyed possessions are not returned to the possession deck, they are removed from play. &
    
    14.25 &
    
    1
    
    \\ \hline
    
    \rn &
    
    If a rebel character is captured, the imperial player may hold to that character’s possessions until the end of play (except spaceships), but may not use them. & 
    
    14.26 &
    
    3
    
    \\ \hline
    
    \rn &
    
    If a possession is being used to receive bonus draws, its use must be declared at the outset of the mission, before drawing any action cards. &
    
    14.27 &
    
    3
    
    \\ \hline
    
    \rn &
    
    Possessions (n49?n52) “Cervac Mk V”, “Norrocks”, “Charsot”, and “Advisor Andriod” are companions. &
    
    14.3 &
    
    1
    
    \\ \hline
    
    \rn &
    
    A companion counts as one passenger on a character spaceship. &
    
    14.3 &
    
    2
    
    \\ \hline
    
    \rn &
    
    Possessions (n41-n42) “High Energy Sniper’s Rifle” and “Assassin’s Blade” are weapons. &
    
    14.4 &
    
    1
    
    \\ \hline
    
    \rn &
    
    Possessions (n43-n48) are objects. & 
    
    14.4 &
    
    1
    
    \\ \hline
    
    \rn &
    
    Weapons and objects do not count towards passenger limits. &
    
    14.4 &
    
    1
    
    \\ \hline
    
    \rn &
    
    Helian Drug lasts from the segment of the Player turn declared to the beginning of the same segment in the phasing player’s next player turn. &
    
    14.4 &
    
    3
    
    \\ \hline
    
    
    
    
    
  \end{longtable}
\end{center}