\section{Search}
\label{sub:search}
% status : finished?

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{\first} | p{\second} | p{\third} | p{\fourth} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric}
    \\ \hline
    
    \rn &
    
    If a military unit finds an enemy unit, squad type combat may be initialized. &
    
    7.1 &
    
    8
    
    \\ \hline
    
    \rn &
    
    Enemy can make a reaction move due to “detected” characters and may conduct a search for those characters during the Search Phase &
    
    9.41 &
    
    6
    
    \\ \hline
    
    \rn &
    
    Characters may be detected due to events on an action card when resolving mission or due to a search. &
    
    9.42 &
    
    4
    
    \\ \hline
    
    \rn &
    
    Non-phasing player may search for "Detected" enemy characters in an environ occupied by his own characters or military units during the search phase. &
    
    11.0 &
    
    9
    
    \\ \hline
    
    \rn &
    
    Non-phasing player may search for enemy characters that are performing missions (Action Event). &
    11.0 &
    
    7
    
    \\ \hline
    
    \rn &
    
    Searching is resolved by using the search table. &
    
    11.0 &
    
    1
    
    \\ \hline
    
    \rn &
    
    Characters stacked with military units cannot be used for searching. &
    
    11.21 &
    
    5
    
    \\ \hline
    
    \rn &
    
    Characters stacked with military units can be unstacked and then the characters can perform a search. &
    
    11.21 &
    
    4
    
    \\ \hline
    
    \rn &
    
    If a character is a leader, that character cannot be used for searching. &
    
    11.22 &
    
    2
    
    \\ \hline
    
    \rn &
    
    Searching by military units and characters must be done separately and is two different searches. &
    
    11.23 &
    
    6
    
    \\ \hline
    
    \rn &
    
    Only the group that successfully searches can attack. &
    
    11.23 &
    
    5
    
    \\ \hline
    
    \rn &
    
    All searching attempts are set before any search procedure is carried out. &
    
    11.23 &
    
    6
    
    \\ \hline
    
    \rn &
    
    When a player uses characters to search, those characters are automatically detected. &
    
    11.31 &
    
    4
    
    \\ \hline
    
    \rn &
    
    Combat is not required in either kind of searching. &
    
    11.32, 11.33 &
    
    2
    
    \\ \hline
    
    \rn &
    
    
    If player decides on combat, combat must be immediate. &
    
    11.34 &
    
    1
    
    \\ \hline
    
    \rn &
    
    Searching can only be done during the search phase of enemy player turn or if called by an action card &
    
    11.1 &
    
    6
    
    \\ \hline
    
    \rn &
    
    If searching is called by an action event, play is interrupted until the searching operation and possible combat is resolved. &
    
    11.12 &
    
    2
    
    \\ \hline
    
    \rn &
    
    Searching can only be done in environs with friendly characters or military units AND detected enemy characters. &
    
    11.1 &
    
    4
    
    \\ \hline
    
    \rn &
    
    Characters stacked with military units cannot be searched. &
    
    11.1 &
    
    5
    
    \\ \hline
    
    \rn &
    
    Characters alone or stacked with other characters and/or spaceships can be searched for. &
    
    11.11 &
    
    7
    
    \\ \hline
    
    \rn &
    
    Searching can be done in any and all environs each search phase that meet the criteria. &
    
    11.1 &
    
    9
    
    \\ \hline
    
    \rn &  
   
   Characters performing a successful search are considered the attacking force. &
   
   12.1 &
   
   3
   
   \\ \hline
   
   \rn &
   
   If an event allowing non-phasing player to conduct search for characters going on the missions, the player searches for one group immediately (Also see [13.42]). &
   
   13.48 &
   
   4
   
   \\ \hline
   
   \newrule{If additional action card is drawn that allows the non-Phasing to search for characters (during the same mission phase as the previous one), the non?Phasing player may search for a mission group that has not been searched for during that mission phase.}{13.48}{-}
   
   \newrule{If all mission groups in an environ has been searched for once (success is not important), no more searches can be conducted.}{13.48}{-}
    
    \newrule{If no more searches can be conducted because all missions groups have already been searched for, the card is ignored.}{13.48}{-}
   
   \newrule{Searching Rebel characters that attack benefit from possessions.}{12.11}{2}
   
   \newrule{If the military units have a leader, the squad’s endurance is increased.}{12.12}{1}
   
   \newrule{Military units are never affected by the outcome of character combats involving squads that they have “dispatched” upon finding enemy characters.}{12.12}{3}
    
  \end{longtable}
\end{center}