\section{Spaceships}

% status : in progress?

\subsection{Rebel Spaceships}

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{.5cm} | p{10.0cm} | p{2.0cm} | p{2.5cm} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric Value}
    \\ \hline
    
    \rn &
    
    Possession cards 33?40 are Rebel Character spaceships. &
    
    14.5 &
    
    - 
    
    \\ \hline
    
    \rn &
    
    The Maneuver rating is used to determine the evasion value during detection routine. &
    
    14.5 &
    
    -
    
    \\ \hline
    
    \rn &
    
    The evasion value is the sum of the spaceship’s maneuver rating and the pilot character’s navigation rating (see 14.53). &
    
    14.5 &
    
    -
    
    \\ \hline
    
    \rn &
    
    The passenger ratings determines the maximum number of characters and companion possessions that the spaceship may carrying when it is being moved. &
    
    14.5 &
    
    -
    
    \\ \hline
    
    \rn &
    
    A spaceship may be assigned and reassigned to any Rebel characters. &
    
    14.51 &
    
    \\ \hline
    
    \rn &
    
    To pilot a starship, the assigned spaceship must have a navigation greater than one. &
    
    14.51 &
    
    -
    
    \\ \hline
    
    \rn &
    
    The pilot is which character possesses the spaceship. &
    
    14.51 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If the ship’s maneuver rating exceeds the pilot’s navigation by more than one, the ship’s maneuver rating is reduced until it is one greater than the pilot’s navigation rating (except for S?XIII spaceship). &
    
    14.52 &
    
    - 
    
    \\ \hline
    
    \rn &
    
    The S?XII spaceship always has its full maneuver rating when determining the evasion rating. &
    
    14.58 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If the pilot’s navigation rating exceeds the ship’s maneuver rating by more than one, the pilot’s navigation rating is reduced until it is one greater than the ship’s maneuver. &
    
    14.52 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If the rebel player receives a character than possess a character spaceship during play, that character’s spaceship is assigned to that player if the spaceship is not in play. &
    
    14.53 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If the rebel player receives a character that possess a character spaceship, the spaceship is assigned to that character. &
    
    14.53 &
    
    -
    
    \\ \hline
    
    \rn &
    
    A rebel player that receives a character spaceship due to receiving the character that is listed as its owner, that spaceship can still be reassigned. &
    
    14.53 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If the character spaceship already exists when the player receives the character, then no effect. &
    
    14.53 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If the owner of the spaceship is killed or captured while in an environ, the spaceship may be immediately reassigned to another character he is stacked with, or stacked with any friendly military units. &
    
    14.55 &
    
    - 
    
    \\ \hline
    
    \rn &
    
    If a character moves during a reaction move, only the pilot and the spaceship may be moved, no other characters. &
    
    14.56 &
    
    -
    
    \\ \hline
    
    \rn &
    
    The number of characters and companion possessions is limited by the ship’s passenger rating. &
    14.57 &
    -
    
    \\ \hline
    
    \rn &
    
    Weapons and object possession do not count towards the passenger limit. &
    
    14.57 &
    
    -
    
    \\ \hline
    
    \rn &
    
    A spaceship cannot carry another spaceship. &
    
    14.57 &
    
    -
    
    \\ \hline
    
    \rn &
    
    Each spaceship must be piloted unless moving with Rebel military units. &
    
    14.57 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If the spaceship is not stacked with Rebel characters or with Rebel military units, it is immediately lost. &
    
    14.59 &
    
    -
    
    \\ \hline 
      
  \end{longtable}
\end{center}

\subsection{Imperial Spaceships}


\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{.5cm} | p{10.0cm} | p{2.0cm} | p{2.5cm} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric Value}
    \\ \hline
    
    \rn &
    
    Redjac’s spaceship can only be piloted by Redjac. &
    
    14.6 &
    
    - 
    
    \\ \hline
    
    \rn &
    
    If Redjac’s spaceship is ever not stacked with Redjac, it is removed from play. &
    
    14.6 &
    
    -
    
    \\ \hline
    
    \rn &
    
    The imperial player may only receive a spaceship if the Imperial player has less spaceships in play than at the beginning of the game. &
    
    14.61 &
    
    -
    
    \\ \hline
    
    \rn &
    
    If the imperial player is eligible to receive a starship, it must be stacked with an Imperial Knight. &
    
    14.61, 15.73 &
    
    -
    
    \\ \hline
    
    \rn &
    
    An Imperial spaceship received by an Imperial Knight at the end of the turn can be reassigned. &
    
    14.62 &
    
    - 
    
    \\ \hline
    
    \rn &
    
    Redjac’s spaceship cannot return to play if lost. &
    
    14.62 &
    
    -
    
    \\ \hline
    
    \rn &
    
    Redjac can receive an Imperial spaceship occurring to the beginning of game turn if his spaceship is lost. &
    
    14.63 &
    
    -
    
    \\ \hline
    
    \rn &
    
    Imperial Spaceships are subject to all the restrictions of Rebel spaceships. &
    
    14.64 &
    
    -
    
    \\ \hline
      
  \end{longtable}
\end{center}