\section{Stacking}

% status : in progress?

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{.5cm} | p{10.0cm} | p{2.0cm} | p{2.5cm} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric Value}
    \\ \hline
    
    \rn &
    
    There is no limit the number of units in a stack (except due to environ size restriction) &
    
    9.5 &
    
    - 
    
    \\ \hline
    
    \rn &
    
    The number of military units in a stack can never exceed the size of the environ size. &
    
    9.5 &
    
    -
    
    \\ \hline
    
    \newrule{A stack can be comprised of characters, military units, and spaceships}{9.5}{-}
    
    \newrule{At the end of the operations phase, an environ may have at most two stacks for each player} {9.5}{-}
    
    \newrule{Before the end of the operations phase, a stack can be comprised of any combination of military units, spaceships, and characters}{9.51}{-}
    
    \newrule{If the stack contains any military units, it is moved according to the military units rules.}{9.52}{-}
    
    \newrule{Stacks with military units attack and are attacked according to military unit rules.}{9.52}{-}
    
    \newrule{A stack with military units are considered detected with regards to enemy PDBs.}{9.52}{-}
    
    \newrule{A character with a leadership of 1 or more in a stack can be named leader.}{9.53}{-}
    
    \newrule{The leader of a stack can be changed at any time to another eligible character.}{9.53}{-}
    
    \newrule{The stack, without any military units, must contain at least one character and can contain any number of spaceships.}{9.54}{-}
    
    \newrule{A stack with more than one spaceship cannot move.}{9.54}{-}
    
    \newrule{A spaceship can only be moved if in a stack with military units or contains a character with a navigation rating of 1 or more.}{9.55}{-}
    
    \newrule{At the end of the movement segment, units should be organized in two stacks: all characters (and their spaceships) that can perform missions and all other units.}
    {9.57}{-}
    
    \newrule{At the end of the movement segment, all characters that are not in the mission stack cannot perform missions that turn.}
    {9.57}{-}
    
    \newrule{If the leader is no longer in the stack, the stack no longer has a leader.}{9.57}{-}
    
  \end{longtable}
\end{center}