\section{Star System Scenarios}

% status : finished?

\setcounter{rc}{0}

\begin{center}

  \begin{longtable}{| p{.5cm} | p{10.0cm} | p{2.0cm} | p{2.5cm} |}
    \hline
    \textbf{\#}&
    \textbf{Rule Description}&
    \textbf{Reference(s)}&
    \textbf{Metric Value}
    \\ \hline
    
    \newrule{Each player may place the characters and spaceships received at start of play on any one environ (on a planet the player controls).}{16.12}{-}
    
    \newrule{If no planets are available, the character and spaceship(s) arrive “from space” and chooses an environ to land on, undergoing possible detection routine.}{16.12}{-}
    
    \newrule{Military units can be placed on any environ on a planet under the player’s control.} {16.13}{-}
    
    \newrule{All friendly units on the same environ are placed in one stack.}{16.13}{-}
    
    \newrule{Mobile imperial units are placed in “mobile” status.}{16.13}{-}
    
    \newrule{Rebel military units must be placed in the same environ as the unit type.}{16.13}{-}
    
    \newrule{The imperial player always places his units first.}{16.14}{-}
    
    \newrule{The rebel player game turn is first.}{16.14}{-}
    
    \newrule{Reinforcements received during the game may be placed on any Environ on any planet the player controls.}{16.15}{-}
    
    \newrule{Reinforcements received during the game may be placed on any Environ with no enemy units on any planet that neither player controls.}{16.15}{-}
    
    \newrule{If the player cannot receive reinforcements due to lack of eligible environ, the player does not receive those reinforcements.}{-}{-}
    
  \end{longtable}
\end{center}